Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-03-26 src/tex/ms.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/abundance_evolution_yields.pdf}
    \caption{Caption}
    \label{fig:abundance-evolution-yields}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models. Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius. A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates from APOGEE stars come from \citet{leung_variational_2023}. Each column shows results from a different multi-zone model: {\bf (a)} a model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with $y/Z_\odot=1$ and greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; and {\bf (d)} a model with $y/Z_\odot=1$ and which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$. {\bf Key takeaway:} All models feature a major dilution event at a lookback time of 9 Gyr, and for models with low yields and outflows the dilution persists throughout much of the thin disk epoch.}
    \label{fig:abundance-evolution}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/abundance_evolution_yields.pdf}
    \caption{Stellar age--abundance relations produced by multi-zone models which assume different yield sets and outflow mass-loading factors. Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq |z| \leq 0.5\,{\rm kpc}$) and is color-coded by its birth radius. A Gaussian scatter has been applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\,{\rm kpc}$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates for APOGEE stars come from \citet{leung_variational_2023}. {\bf Key takeaway:} Both models feature a major dilution event at a lookback time of 9 Gyr, and for model (a) the dilution persists throughout much of the thin disk epoch.}
    \label{fig:abundance-evolution-yields}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}. The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
    \label{fig:abundance-evolution-params}
\end{figure*}
